\begin{rubric}{Miscellaneous Experience}
%\subrubric{UG projects Supervised}
 %\entry*[Meera P R, ]
%\textbf{ENERGY HARVESTING FLOOR TILES}, \ 
%Cost-effective electricity-generating floor tiles \\
%capable of producing electricity from human foot pressure efficiently.
 %  \entry*[Akhil john Paul, Arjun M.G, Basil  .M. jacob, Basil  S]
 % \textbf{GREEN CHANNEL IDEA FOR TRFFIC CONTROL}, This project works for the utilizing the kinetic energy of a running vehicle. The kinetic energy is converted into electrical energy by using dynamo. Smart traffic monitoring is operated by using the generated energy.
   % \entry*[2016-17]
   % \textbf{Merit Award}, Received the "Award of Excellence" for outstanding performance in ICET during academic year.



%\entry*[2022 July- 2022 August]%
	%\textbf{Certification.~NPTEL:} Brief Introduction to Psychology.\par
 
\subrubric{UG projects Supervised}
\entry*[Meera P R\\ Melcy Francis\\Treesa Joseph ] \textbf{ENERGY HARVESTING FLOOR TILES},  Cost-effective electricity-generating floor tiles capable of producing electricity from human foot pressure efficiently.\par
\entry*[Akhil john Paul\\ Arjun M.G\\Basil  .M. jacob\\Basil  S ] \textbf{GREEN CHANNEL IDEA FOR TRAFFIC CONTROL},  This project works for the utilizing the kinetic energy of a running vehicle. The kinetic energy is converted into electrical energy by using dynamo. Smart traffic monitoring is operated by using the generated energy\par

\subrubric{PG projects Supervised}
\entry*[Muhseena T K ] \textbf{Multipitch Estimaation},  Project proposed a new approach for estimating the pitch frequency of a sound signal based on wavelet packet transform and cepstrum method.\par
\entry*[Rakhi E R] \textbf{Single Channel Speech Separation}, These systems separate the target speech from the noisy speech\par
\entry*[2020] \textbf{Enabling Entrepreneurship and Startup},  NITTTR,Chennai,October 17-21, 2022.\par
\entry*[2021] \textbf{Sustainable Engineering Practices in Agriculture and Automotive Industry}, M A College of Engineering, Kothamangalam ,May 17-21, 2021.\par
\entry*[2021] \textbf{Embedded Systems},  College of Engineering Kidangoor,March 3-6, 2021.\par
\entry*[2021] \textbf{Professional Ethics in current pandemic scenario},  College of Engineering Perumon,Feb, 22-27, 2021.\par



\subrubric{Workshops}
\entry*[2022] \textbf{Introduction to GNU Radio},  College of
Engineering Attingal. July 2, 2022.
\subrubric{Conferences}
\entry*[2026] \textbf{IEDC STARTUP SUMMIT 2026},  AMALJYOTHI COLLEGE OF ENGINEERING, Kanjirapally  March 7, 2026.
\entry*[2025] \textbf{IEDC SUMMIT 2025},  NIT, Calicut, October 12, 2025
\entry*[2023] \textbf{IEDC SUMMIT 2023},  College of Engineering, Trivandrum October 12, 2023
\entry*[2023] \textbf{IEDC SUMMIT 2023},  Rajagiri School of Engineering and Technology, Ernakulam. March 3 2023
\entry*[2022] \textbf{IIC regional Meet 2022},  KMEA engineering College Kochi, August 6, 2022.
\entry*[2022] \textbf{IEDC SUMMIT 2022},  St. Joseph College of Engineering Pala, March 5, 2022.


\subrubric{Presentation/Poster Presentation }
\entry*[2017] \textbf{Hands on Workshop on Android in Dec 2017},  Ilahia College of Engineering and Technology.

\subrubric{Duties/Responsibilities }
\entry*[2023] \textbf{Nodal officer of KIRF}
\entry*[2022] \textbf{Nodal officer of AISHE}
\entry*[2021] \textbf{IEDC Nodal officer}
\entry*[2020] \textbf{Research and
Development cell }
\entry*[2020] \textbf{In charge of AICTE
related matters }
\entry*[2020] \textbf{Overall in charge of
NBA Criteria 8 of the College }
%\end{rubric}
\subrubric{Books Published }
\entry*[2024] \textbf{A Brief introduction to Entrepreneurship and IPR},  2024 
\subrubric{Certifications }
\entry*[2022] \textbf{NPTEL Certification}, Introduction to psychology , 2022 
\entry*[2025] \textbf{Wadhwani Foundation  certificate}, Certified Entrepreneurship Educator , 2025
\end{rubric}
